An Overview of Distributed Version Control Systems

### 2010-07-03 laarsample.tex
reubicada la seccion Possible Workflows
Pequeño fix en la sección Tool Support
Mejorada la redacción de la sección Trust Based Securirty

%Arq | mejorar redaccion
\subsection{Trust Based Security}
Security on DVCS is based on the "circle of trust" model, which implies that you trust only on a very specific group of people and you only pull from their repositories. They, in turn, have their own group of trust and only pull from that other group. This creates a chain of trust so that even if you don't trust someone directly by scalating their changes you could end up having his code only after it has been reviewed by the people you really trust.

@@

There are many other third-party GUIs for Git, but none of them has all available operations nor are they equally mature. 
In those cases, going back to the command line is the only way to do them. One of the most complete GUIs is SmartGit, but 
it requires to purchase a (rather inexpensive) licence for commercial usage. An alternative for Windows only 
is Tortoise-Git, which is a fork of Tortoise-SVN that shares the same look-and-feel, while supporting most of the 
Git operations. There are others GUIs but they are either very incomplete or are not really mature and have 
some kind of bugs (like git-cola) \cite{interfaces}.

There are some tools to interoperate with others VCS, easing transitions.
Git in particular includes has git-svn which allows to push and pull from svn repositories.

% Intercalar tortoise con tortoise-git y el del svn con el svn
Mercurial has similar tools, incluing hg-subversion to interact with svn repositories, and Tortoise-Hg which is
the equivalent of Tortoise-Git.
%----------------------------------------------------------------------

% Reveer de mover esta sección antes de la comparacion
\section{POSSIBLE WORKFLOWS}
\label{WORKFLOWS}

@@

>>>>

\subsection{Trust Based Security}
Security on DVCS is based on the "circle of trust" model. This model proposes that a developer should only pull changes from a specific group of people
in which she trusts. This people have, at the same time, their own group of trust from which they pull. Following this chain any change could scalate
to any repository, provided that someone trustworthy has reviewed it.

@@

%----------------------------------------------------------------------

\section{POSSIBLE WORKFLOWS}
\label{WORKFLOWS}

@@

There are many other third-party GUIs for Git, but none of them has all available operations nor are they equally mature. 
In those cases, going back to the command line is the only way to do them. One of the most complete GUIs is SmartGit, but 
it requires to purchase a (rather inexpensive) licence for commercial usage. An alternative for Windows only 
is Tortoise-Git, which is a fork of Tortoise-SVN that shares the same look-and-feel, while supporting most of the 
Git operations. There is also a Tortoise-Hg to work with Mercurial DVCS.
There are others GUIs but they are either very incomplete or are not really mature and have 
some kind of bugs (like git-cola) \cite{interfaces}.

There are some tools to interoperate with others VCS, easing transitions.
Git in particular includes has git-svn which allows to push and pull from svn repositories. This is also available for Mercurial DVCS
with the hg-subversion project.
